Species richness and food-web structure jointly drive community biomass and its temporal stability in fish communities

### 2021-02-19 manuscript/bef_stability/manuscript.Rmd
Minor edits

As classically found in studies considering a single trophic level,
[@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020],
asynchrony in population temporal variations also explains a significant part
of the stabilizing effects of species richness on community biomass in food-webs
[@thebault_trophic_2005]. Indeed, a low synchrony in population fluctuations,
i.e. asynchrony, is synonymous of compensatory dynamics, where the decrease in
abundance of a population is compensated by the increase of another. However,
higher connectance can counterbalance the positive effects of species
richness on temporal stability of community biomass, by leading to a negative
relationship between species richness and population temporal variability
[@thebault_trophic_2005]. In addition, the presence of species at higher trophic
levels increases total primary production, through stronger top-down effects
associated with higher nutrient uptake [@wang_biodiversity_2018]. The addition of predators has
also cascading effects on both population variability and
synchrony at lower trophic levels [@teng_dynamics_2004;
@shanafelt_stability_2018]. Overall, these theoretical studies show that the
effects of species richness and food-web structure, such as connectance and
average trophic level, are potentially conflicting or synergistic in such a way
that they need to be addressed jointly.

>>>>

As classically found in studies considering a single trophic level,
[@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020],
asynchrony in population temporal variations also explains a significant part
of the stabilizing effects of species richness on community biomass in food-webs
[@thebault_trophic_2005]. Indeed, a low synchrony in population fluctuations,
i.e. asynchrony, is synonymous of compensatory dynamics, where the decrease in
abundance of a population is compensated by the increase of another. However,
higher food-web connectance can counterbalance the positive effects of species
richness on temporal stability of community biomass, because it may increase
competition between consumers and then leads to a positive relationship between
species richness and population temporal variability
[@thebault_trophic_2005]. In addition, the presence of species at higher trophic
levels increases total primary production, through stronger top-down effects
associated with higher nutrient uptake [@wang_biodiversity_2018]. The addition of predators has
also cascading effects on both population variability and
synchrony at lower trophic levels [@teng_dynamics_2004;
@shanafelt_stability_2018]. Overall, these theoretical studies show that the
effects of species richness and food-web structure, such as connectance and
average trophic level, are potentially conflicting or synergistic in such a way
that they need to be addressed jointly.
